---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# addNarrData

<!-- badges: start -->
[![R build status](https://github.com/geomarker-io/addNarrData/workflows/R-CMD-check/badge.svg)](https://github.com/geomarker-io/addNarrData/actions)
<!-- badges: end -->

The goal of addNarrData is to add average NARR weather varaibles to your data based on `narr_cell` (an identifier for a 12 x 12 km NARR grid cell) and `start_date` and `end_date`. 

## Installation

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("geomarker-io/addNarrData")
```

### NARR database file

The NARR values are stored in `narr.fst` (20 GB in size), which can either be located in the working directory, or preferably within the platform-specific user data directory so it can be shared across R sessions and projects. If needed, you will be prompted to run `download_narr_fst()` the first time you call `get_narr_data()`. This 20 GB file is a large file to download, but will only need to be done once per user and computer.

## Example

Get NARR cell numbers.

```{r}
library(addNarrData)
library(magrittr)

d <- tibble::tibble(
  id = c('1a', '2b', '3c'),
  visit_date = c("3/8/17", "2/6/12", "6/18/20"),
  lat = c(39.19674, 39.19674, 39.48765),
  lon = c(-84.582601, -84.582601, -84.610173)
) %>%
  dplyr::mutate(
    visit_date = as.Date(visit_date, format = "%m/%d/%y"),
    start_date = visit_date - lubridate::days(7), # weekly average
    end_date = visit_date
  )

d_narr_cell <- get_narr_cell_numbers(d)
```

Add NARR data.

```{r, eval = F}
download_narr_fst()
```

NARR Data Dictionary
| Variable Name | Description|
| :-- | :-- |
| hpbl | Planetary Boundary Layer Height |
| vis | Visibility |
| uwnd.10m | U Wind Speed at 10m |
| vwnd.10m | V Wind Speed at 10m |
| air.2m | Air Temperature at 2m |
| rhum.2m | Humidity at 2m |
| prate | Precipitation Rate |
| pres.sfc | Surface Pressure |

More information is available at the [NOAA](https://www.ncdc.noaa.gov/sites/default/files/attachments/ncdc-narrdsi-6175-final.pdf) website.

```{r}
get_narr_data(d_narr_cell, narr_variables = c('air.2m', 'rhum.2m'))
```

