---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# addNarrData

<!-- badges: start -->
[![R build status](https://github.com/geomarker-io/addNarrData/workflows/R-CMD-check/badge.svg)](https://github.com/geomarker-io/addNarrData/actions)
<!-- badges: end -->

The goal of addNarrData is to add average NARR weather varaibles to data based on `narr_cell` (an identifier for a 12 x 12 km NARR grid cell) and `start_date` and `end_date`. 

NARR Data Dictionary

| Variable Name | Description|
| :-- | :-- |
| hpbl | Planetary Boundary Layer Height |
| vis | Visibility |
| uwnd.10m | U Wind Speed at 10m |
| vwnd.10m | V Wind Speed at 10m |
| air.2m | Air Temperature at 2m |
| rhum.2m | Humidity at 2m |
| prate | Precipitation Rate |
| pres.sfc | Surface Pressure |

More information is available at the [NOAA](https://www.ncdc.noaa.gov/sites/default/files/attachments/ncdc-narrdsi-6175-final.pdf) website.

## Installation

Install from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("geomarker-io/addNarrData")
```

## Example Usage

add NARR data.

```{r}
library(addNarrData)
library(magrittr)

d <- tibble::tibble(
  id = c('1a', '2b', '3c'),
  visit_date = c("3/8/17", "2/6/12", "6/18/20"),
  lat = c(39.19674, 39.19674, 39.48765),
  lon = c(-84.582601, -84.582601, -84.610173)
)

d %>%
  dplyr::mutate(
    visit_date = as.Date(visit_date, format = "%m/%d/%y"),
    start_date = visit_date - lubridate::days(7), # weekly average
    end_date = visit_date
    ) %>%
  get_narr_data(narr_variables = c("air.2m", "rhum.2m"))
```

### NARR data files

The package works by downloading chunks of NARR data automagically. These are stored in an Amazon s3 drive at 

```
s3://geomarker/narr/narr_chunk_fst/narr_chunk_{number}_{variable}.fst
```

where `{number}` is replaced with the NARR chunk number  (0 - 9), and `{variable}` is replaced with one of the available NARR variables (`hpbl`, `vis`, `rhum.2m`, `prate`, `air.2m`, `pres.sfc`, `uwnd.10m`, `vwnd.10m`). Each file is about 350 MB in size, but only the files needed will be downloaded.

More information on the NARR fst chunk files can be found at [narr_raster_to_fst](https://github.com/geomarker-io/narr_raster_to_fst#narr_raster_to_fst).

